MENU FILE #6 (EXPERIMENT DESIGNS)--
 
0                  0       200
Design of Experiment Files
1                  0       216
Comparative Designs--Latin Square & Graeco-Latin Square
2                  0       226
2**k Full Factorial Designs
3                  0       237
2**(k-p) Fractional Factorial Designs/8 or Fewer Factors
4                  0       257
2**(k-p) Fractional Factorial Designs/9 or More Factors
5                  0       276
Plackett-Burmann 12-Run Design
6                  0       282
Taguchi Designs
7                  0       304
Response Surface/Optimization Designs
8                  0       316
Random Permutations
9                  0       330
Index of Design and Examples
10                 0       339
Example of Usage of the Design of Experiment Files--
11                 0       367
Example #2 of Usage of the Design of Experiment Files--
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
----------------------------------------
 
0
Design of Experiment Files
   1. Comparative Designs--Latin Square & Graeco-Latin Square
   2. 2**k Full Factorial Designs/8 or Fewer Factors
   3. 2**k Full Factorial Designs/9 or More Factors
   4. 2**(k-p) Fractional Factorial Designs
   5. Plackett-Burmann 12-Run Design
   6. Taguchi Designs
   7. Response Surface/Optimization Designs
   8. Random Permutations
   9. Index of Design and Examples
  10. Example #1 of Usage of the Design of Experiment Files
  11. Example #2 of Usage of the Design of Experiment Files
 
----------------------------------------
 
1
Comparative Designs--Latin Square & Graeco-Latin Square
      LATSQ3.DAT    Latin sq exp des 3 factors, 3 levels, 9 runs
      LATSQ4.DAT    Latin sq exp des 3 factors, 4 levels, 16 runs
 
      GRLATSQ3.DAT  Graeco-Latin sq exp des 4 fac, 3 lev, 9 runs
      GRLATSQ4.DAT  Graeco-Latin sq exp des 4 fac, 4 lev, 16 runs
 
----------------------------------------
 
2
2**k Full Factorial Designs
      2TO2.DAT      Full factor exp des 2 lev,  2 fac,   4 runs
      2TO3.DAT      Full factor exp des 2 lev,  3 fac,   8 runs
      2TO4.DAT      Full factor exp des 2 lev,  4 fac,  16 runs
      2TO5.DAT      Full factor exp des 2 lev,  5 fac,  32 runs
      2TO6.DAT      Full factor exp des 2 lev,  6 fac,  64 runs
      2TO7.DAT      Full factor exp des 2 lev,  7 fac, 128 runs
 
----------------------------------------
 
3
2**(k-p) Fractional Factorial Designs/8 or Fewer Factors
      2TO3M1.DAT    Frac factor exp des 2 lev,  3 fac,   4 runs
      2TO4M1.DAT    Frac factor exp des 2 lev,  4 fac,   8 runs
      2TO5M2.DAT    Frac factor exp des 2 lev,  5 fac,   8 runs
      2TO5M1.DAT    Frac factor exp des 2 lev,  5 fac,  16 runs
      2TO6M3.DAT    Frac factor exp des 2 lev,  6 fac,   8 runs
      2TO6M2.DAT    Frac factor exp des 2 lev,  6 fac,  16 runs
      2TO6M1.DAT    Frac factor exp des 2 lev,  6 fac,  32 runs
      2TO7M4.DAT    Frac factor exp des 2 lev,  7 fac,   8 runs
      2TO7M3.DAT    Frac factor exp des 2 lev,  7 fac,  16 runs
      2TO7M2.DAT    Frac factor exp des 2 lev,  7 fac,  32 runs
      2TO7M1.DAT    Frac factor exp des 2 lev,  7 fac,  64 runs
      2TO8M4.DAT    Frac factor exp des 2 lev,  8 fac,  16 runs
      2TO8M3.DAT    Frac factor exp des 2 lev,  8 fac,  32 runs
      2TO8M2.DAT    Frac factor exp des 2 lev,  8 fac,  64 runs
      2TO8M1.DAT    Frac factor exp des 2 lev,  8 fac, 128 runs
 
----------------------------------------
 
4
2**(k-p) Fractional Factorial Designs/9 or More Factors
      2TO9M5.DAT    Frac factor exp des 2 lev,  9 fac,  16 runs
      2TO9M4.DAT    Frac factor exp des 2 lev,  9 fac,  32 runs
      2TO9M3.DAT    Frac factor exp des 2 lev,  9 fac,  64 runs
      2TO9M2.DAT    Frac factor exp des 2 lev,  9 fac, 128 runs
      2TO10M6.DAT   Frac factor exp des 2 lev, 10 fac,  16 runs
      2TO10M5.DAT   Frac factor exp des 2 lev, 10 fac,  32 runs
      2TO10M4.DAT   Frac factor exp des 2 lev, 10 fac,  64 runs
      2TO10M3.DAT   Frac factor exp des 2 lev, 10 fac, 128 runs
      2TO11M7.DAT   Frac factor exp des 2 lev, 11 fac,  16 runs
      2TO11M6.DAT   Frac factor exp des 2 lev, 11 fac,  32 runs
      2TO11M5.DAT   Frac factor exp des 2 lev, 11 fac,  64 runs
      2TO11M4.DAT   Frac factor exp des 2 lev, 11 fac, 128 runs
      2TO15M11.DAT  Frac factor exp des 2 lev, 11 fac,  16 runs
      2TO31M26.DAT  Frac factor exp des 2 lev, 31 fac,  32 runs
 
----------------------------------------
 
5
Plackett-Burmann 12-Run Design
      PLACBURM.DAT  Plack-Burm orth exp des 11 factors, 2 levels
 
----------------------------------------
 
6
Taguchi Designs
      L4.DAT        Tag. L4   orth exp des  3 factors,   2 lev
      L8.DAT        Tag. L8   orth exp des  7 factors,   2 lev
      L9.DAT        Tag. L9   orth exp des  4 factors,   3 lev
      L12.DAT       Tag. L12  orth exp des 11 factors,   2 lev
      L16.DAT       Tag. L16  orth exp des 15 factors,   2 lev
      L16B.DAT      Tag. L16B orth exp des  5 factors,   4 lev
      L18.DAT       Tag. L18  orth exp des  7 factors, 6/3 lev
      L25.DAT       Tag. L25  orth exp des  6 factors,   5 lev
      L27.DAT       Tag. L27  orth exp des 13 factors, 2/3 lev
      L32.DAT       Tag. L32  orth exp des 31 factors,   2 lev
      L32B.DAT      Tag. L32B orth exp des 10 factors, 2/4 lev
      L36.DAT       Tag. L36  orth exp des 22 factors,   3 lev
      L50.DAT       Tag. L50  orth exp des 12 factors, 2/5 lev
      L54.DAT       Tag. L54  orth exp des 26 factors, 2/3 lev
      L64.DAT       Tag. L64  orth exp des 31 factors,   2 lev
      L64B.DAT      Tag. L64B orth exp des 21 factors,   4 lev
      L81.DAT       Tag. L81  orth exp des 40 factors,   3 lev
 
----------------------------------------
 
7
Response Surface/Optimization Designs
      2TO2WC.DAT    2**2 factor exp des with 2 cen pts 2 fac 3 lev
      STAR2WC.DAT   2-dim star exp des  with 2 cen pts 2 fac 3 lev
      CC2.DAT       2-dim central composite exp des    2 fac 5 lev
 
      2TO3WC.DAT    2**3 factor exp des with 3 cen pts 3 fac 3 lev
      STAR3WC.DAT   3-dim star exp des  with 3 cen pts 3 fac 3 lev
      CC3.DAT       3-dim central composite exp des    3 fac 5 lev
 
----------------------------------------
 
8
Random Permutations
      PERM9.DAT     Random permutations of 1-9    (Exp. Des.)
      PERM16.DAT    Random permutations of 1-16   (Exp. Des.)
      PERM20.DAT    Random permutations of 1-20   (Exp. Des.)
      PERM30.DAT    Random permutations of 1-30   (Exp. Des.)
      PERM50.DAT    Random permutations of 1-50   (Exp. Des.)
      PERM100.DAT   Random permutations of 1-100  (Exp. Des.)
      PERM200.DAT   Random permutations of 1-200  (Exp. Des.)
      PERM500.DAT   Random permutations of 1-500  (Exp. Des.)
      PERM1000.DAT  Random permutation  of 1-1000 (Exp. Des.)
 
----------------------------------------
 
9
Index of Design and Examples
      TAGINDEX.DAT  Tag. orth exp des--ordered by fact/runs/lev
      2KINDEX.DAT   2**(k-p) exp des--ordered by factors & runs
      BOXHHEX.TEX   Exp des examples from Box, Hunter & Hunter
      BARKEREX.TEX  Exp des examples from Barker (Qual by E. D.)
 
----------------------------------------
 
10
Example of Usage of the Design of Experiment Files--
      The goal is to create an experimental plan consisting
      of 4 factors--each at 2 levels-- and with a total of 8
      runs.  A 2**(4-1) fractional factorial design is
      appropriate--read in the design from 2TO4M1.DAT .
      Every design should have randomized run sequence;
      therefore, we also want to read in a random run
      sequence (say from PERM9.DAT which contains a random
      permutation of 1 to 9), trim it back to a rndom
      permutation of 1 to 8. Finally, print out (to both
      screen and to file OUT.) the design and the random run
      sequence.
 
      LIST 2TO4M1.DAT;. (to view file to see how many lines to skip)
      SKIP 50
      READ 2TO4M1.DAT X1 X2 X3 X4
      LIST PERM9.DAT;. (to view file to see how many lines to skip)
      SKIP 0; ROW LIMITS 26 28; COLUMN LIMITS 1 5
      SERIAL READ PERM9.DAT SEQ
      DELETE SEQ SUBSET SEQ > 8.5
      SET WRITE DECIMALS 0
      WRITE SEQ X1 X2 X3 X4
      WRITE OUT. SEQ X1 X2 X3 X4
 
 
----------------------------------------
 
11
Example #2 of Usage of the Design of Experiment Files--
      The goal is to create an experimental plan consisting
      of 6 factors--each at 2 levels-- and with a total of
      16 runs.  A 2**(6-2) fractional factorial design is
      appropriate--read in the design from 2TO6M2.DAT .
      Every design should have randomized run sequence;
      therefore, we also need a random run sequence (in this
      example, we will generate a random permutation of 1 to
      16 from Dataplot's RANDOM PERMUTATION subcommand under
      LET.  Finally, print out (to both screen and to file
      OUT.) the design and the random run sequence.
 
      LIST 2TO6M2.DAT;. (to view file to see how many lines to skip)
      SKIP 50
      READ 2TO6M2.DAT X1 X2 X3 X4 X5 X6
      LET SEQ = RANDOM PERMUTATION FOR I = 1 1 16
      SET WRITE DECIMALS 0
      WRITE SEQ X1 X2 X3 X4 X5 X6
      WRITE OUT. SEQ X1 X2 X3 X4 X5 X6
 
