MENU FILE #7 (TUTORIAL)
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
----------  *TUTORIAL*  ------------------
 
0
Tutorial
   1. Time Series/Data Plot (DATAPLOT.DP)
   2. Mathematics/Derivative Plot (DERIVPLO.DP)
   3. 1-Factor Modeling/Box Plot (BOXPLOT.DP)
   4. 1-Factor Modeling/Box Plot (BOXPLOT2.DP)
   5. Word Chart/Mathematics Operations (MATHOPER.DP)
 
   6. Autocorrelation Analysis/Lag Plot (LAGPLOT.DP)
   7. Time Series Analysis/Spectral Plot (SPECPLOT.DP)
   8. Regression Analysis/Residual Plot (RESPLOT.DP)
   9. Time Series Smoothing/FFT Plot (FFTPLOT.DP)
  10. Interlab Analysis/Youden Plot (YOUDPLOT.DP)
 
  11. Mathematics/Function Plot for Roots (ROOTPLOT.DP)
  12. Multivariate Analysis/Star Plot (STARPLOT.DP)
  13. 1-Factor Modeling/Mean Plot (MEANPLOT.DP)
  14. 1-Factor Modeling/Stan. Dev. Plot (SDPLOT.DP)
  15. Time Series/Spike Plot (SPIKEPLO.DP)
 
  16. Geographic Analysis/Map Generation (TEXASMAP.DP)
  17. Comparing 2 Dist./Quantile-Quantile Plot (QUANPLOT.DP)
  18. Probability/Prob. Dens. Function Plot (PDFPLOT.DP)
  19. Reliability Analysis/Weibull Plot (WEIBPLOT.DP)
  20. Distributional Analysis/Histogram (HIST.DP)
 
  21. Comparing 2 Dist./Bihistogram (BIHIST.DP)
  22. Multivariate Analysis/Profile Plot (PROFPLOT.DP)
  23. 3-Factor Modeling/GANOVA (GANOVA3.DP)
  24. Multi-Response Analysis/Multi-Trace Plot (MULTITRA.DP)
  25. Presentation Graphics/3-D Bar Histogram (HIST2.DP)
 
To execute any tutorial, enter CALL followed by the name
of the DATAPLOT macro, as in
      CALL DATAPLOT.DP    for the first tutorial
      CALL DERIVPLO.DP    for the second tutorial
      CALL BOXPLOT.DP     for the third tutorial
                          etc.
